\input{template.tex}

\begin{document}
    \maketitle

    \begin{thm}{}{}
        Suppose the edges $e_1,\dots, e_m$ are sorted by their cost. Show how to solve MCP in time $O(n+m)$.
    \end{thm}
    \begin{proof}[Solution]
        The algorithm is executed in iterations. Suppose that $c(e_1)\geq c(e_2)\geq\dots\geq c(e_m)$. In iteration $i$, consider $e_i$. 
        
        There is a set of vertices which is reachable from $s$, and the initial status of the set is $\{s\}$. 
        Each vertex has an predecessor recording the predecessor in the path by which $s$ reaches the vertex. Its initial status is $null$. 
        Each vertex also has a set of unresolved edges whose start point is the vertex. Its initial status is $\emptyset$.
        
        In each iteration, denote the edge we are handling by $e=(u,v)$. 
        
        If $u$ is not reachable, simply add $e$ into the unresolved edge set of $u$. 
        
        If $u,v$ are already reachable, nothing needs to be done. 
        
        If $u$ is already reachable but $v$ is not, set $v$ reachable and set its predecessor to $u$. 
        Then handle all unresolved edges of $v$. (Let the end point of each edge be reachable if it is not.)
        Since this may introduce new reachable vertices, handle them too. This procedure is like a BFS. 
        
        Once $t$ is reached, the algorithm terminates, and the cost of the newly introduced edge is the cost of MCP. 
        Using the predecessor of each vertex, the maximum capacity path from $s$ to $t$ can be generated.
    \end{proof}
    
    \bigskip
    
    First prove that each vertex in the reachable set is really reachable(so it is well-defined): 
    \begin{proof}[Proof]
        The reachable set has the property that, except for $s$, all vertices in the set have a predecessor also in the set. 
        
        This is trivial since when we add a vertex to the reachable set, we set its predecessor by a reachable vertex. 
        
        Using this property, since its predecessor is reachable, the vertex itself is reachable as well. 
    \end{proof}
    
    \bigskip
    
    Then prove that all reachable vertices using $\{e_1,\dots e_n\}$ are in reachable set after iteration $n$: 
    \begin{proof}[Proof]
        Assume that there is a path from $s$ to $v$ using edges $e_{i_1},e_{i_2}\dots e_{i_k},(i_1,i_2\dots i_k\in \{1,2,\dots n\})$. 
        And $\forall j\in \{1,2\dots k\},e_{i_j}=(u_j,u_{j+1});u_1=s,u_{k+1}=v$. 
        Let $M_j=\max\{i_1,i_2\dots i_j\}$, $m_j=\min\{i_1,i_2\dots i_j\}$
        
        Assume that after iteration $M_{q-1}$ $u_1,u_2\dots u_q$ are in reachable set and $u_q$ is added in iteration $M_{q-1}$. 
        If $i_q<M_{q-1}$, $e_q$ is in unresolved set of $u_q$. 
        So in iteration $M_{q-1}=M_q$, when adding $u_q$ in reachable set, 
        all unresolved edges of $u_q$ are handled so $u_{q+1}$ is added as well. 
        If $i_q>M_{q-1}$, in iteration $M_q=i_q$, $u_q$ is in reachable set so $u_{q+1}$ is added in reachable set. 
        
        Consider the initial status that after iteration $M_1=i_1$, $u_1=s,u_2$ are in reachable set and $u_2$ is added in iteration $M_1$. 
        
        By induction, it is proved that after iteration $M_k$, $u_1,u_2\dots u_{k+1}$ are all in reachable set. 
    \end{proof}
    
    \bigskip
    
    
    Now it is trivial to prove the correctness of the algorithm: 
    
    If the cost of MCP is $c^*=e_n$, then the path only uses edges in $\{e_1,\dots e_n\}$, so exactly in iteration $n$, $t$ is reachable. 
    
    Then prove the complexity of the algorithm is $O(n+m)$:
    \begin{proof}[Proof]
        Consider an arbitrary edge $e_k=(u,v)$. If in iteration $k$, $u$ is already reachable, 
        it is not added into the unresolved set so it will not be visited. 
        Otherwise, it is added into the unresolved set of $u$, 
        and when $u$ is added into the reachable set, it will then be visited. 
        
        Since $u$ can only be added to reachable set once, $e_k$ is visited at most twice. So the complexity is $O(m)$.
        
        In the initial step, each vertex is initialized, so the complexity is $O(n)$. 
        
        Combine the two steps together, the total complexity is $O(n+m)$. 
    \end{proof} 

    \newpage
    
    \begin{thm}{}{}
        Give an algorithm for MCP of running time $O(m\log\log m)$.
    \end{thm}
    \begin{proof}[Solution]
        \ 
        
        \begin{algorithm}
            \caption{An algorithm for MCP problem.}
            \begin{algorithmic}
                %\Require edges $e_1,\ldots,e_m$
                \Function{MCP}{$V, E = \{e_1, e_2, \ldots, e_m\}, c$}
                \State $C\gets \{e_1,\ldots,e_m\}$
                \State $oldEdges \gets \emptyset$
                \State $d\gets 0$
                \While{there are multiple capacities of the edges in $C$} \Comment{Loop 1}
                \State $divisions\gets [C]$ \Comment Let $divisions$ be a list only containing the set $C$.
                \For{$i=1$ to $2^{d}$} \Comment{Loop 2}
                
                \State Let $S_1, S_2, \ldots, S_k$ denote the edge sets in $divisions$ in order, i.e., representing $divisions$ as $[S_1, \ldots, S_k]$.
                \State Use median-of-medians algorithm $k$ times to find the median capacity of the capacities of the edges in each set(if there are two medians, choose the larger one). Denote them as $m_1, m_2, \ldots, m_k$ respectively.
                %\State $m_{1},\cdots,m_{k}\gets$ the median of $S_1,\cdots,S_k$ in means of weight
                
                \State $newDivisions \gets [\ ]$ \Comment Let $newDivisions$ be an empty list.
                \For{$j = 1$ to $k$} \Comment{Loop 3}
                \State Append $\{s\in S_{j}:c(s) \geqslant m_{j}\}$ to $newDivisions$.
                \State Append $\{s\in S_{j}:c(s) < m_{j}\}$ to $newDivisions$.
                %\State $divisions\gets \bigcup\limits_{j=1}^{k} \{s\in S_{j}:c(s)<=m_{j}\}\cup \{s\in S_{j}:c(s)>m_{j}\}$
                \EndFor
                \State $divisions \gets newDivisions$
                \EndFor
                \State $C, oldEdges\gets$ \Call{GetDivision}{$divisions$, $oldEdges$} %$GetDivision(divisions)$.
                \State $d\gets 2^{d}+d$
                \EndWhile
                \State \Return the capacity of the edges in $C$
                \EndFunction
                
                \bigskip
                
                \Function{GetDivision}{$divisions$, $oldEdges$} \Comment Using the algorithm of exercise 1.
                \State $G\gets (V, oldEdges)$
                
                \For {$div$ in $divisions$ in the order of the list} %(iterate from higher capacity to lower capacity)
                \State Add all edges in $div$ to $G$.
                \If{$t$ is now reachable from $s$}%\If{$G$ is s-t-connected}
                \State \Return $div$, $oldEdges$
                \Else
                \State $oldEdges \gets oldEdges \cup div$
                \EndIf
                \EndFor
                \EndFunction
            \end{algorithmic}
        \end{algorithm}
        
        {\bf The pseudocode of the algorithm is in the next page.}
        
        The correctness of the algorithm comes from below.
        First, we initialize our $c^*$ candidates to be all capacities of the edges in $G$.
        Then, in each iteration, we divide it into many divisions of approximately the same size in order, and test which division $c^*$ is in.
        Finally, there will be only one candidate left, and the only candidate is $c^*$.
        
        Now we'll analyze the running time.
        Note that using median-of-medians algorithm to find the median of a set $S$ has running time $O(|S|)$.
        In ``Loop 2'' of function \textsc{MCP}, we find the median of $S_1,\ldots,S_k$ in $2^d$ iterations.
        Note that there is an invariant equation $\sum_{i=1}^{k}|S_k|=|C|$.
        So finding the median requires $O(|C|\cdot 2^{d})$ in total.
        The \textsc{GetDivision} function may need to add all the edges into the graph in the worst case.
        Testing the connectivity will use $O(m)$ time in total if we record a set of reachable vertices as decribed in Exercise 1.
        So the running time of \textsc{GetDivision} is $O(m)$.
        
        %Observe that $|C|\cdot 2^{d}=O(m)$.
        We now prove that $|C|\cdot 2^{d}=O(m)$ by induction.
        Initially, $|C|=m$ and $d=0$.
        It obviously holds.
        Suppose $|C_{old}|\cdot 2^{d_{old}}=O(m)$.
        We have $|C_{new}|=O(|C_{old}|\cdot (\frac{1}{2})^{2^{d_{old}}})$,
        $d_{new}=d_{old}+2^{d_{old}}$.
        So  $|C_{new}|\cdot 2^{d_{new}}=O(m)$.
        
        Now we know that a single iteration of ``Loop 1'' takes time $O(m)$.
        Note that $2^{d}\leqslant m$.
        Since $d$ increases exponentially, ``Loop 1'' will iterate $O(\log^*m)$ times.
        Finally, we get the running time is $O(m\log^*m)$.
        Obviously this algorithm has a better running time than $O(m\log\log m),O(m\log\log\log m),O(m\log\log\log\log m)$ when $m$ is sufficiently large.
    \end{proof}
    
    \begin{thm}{}{}
        Give an algorithm for MCP that runs in $O(m\log\log\log m)$? How about $O(m\log\log\log\log m)$?
        How far can you get?
    \end{thm}
    \begin{proof}[Solution]
        See Problem 2.
    \end{proof}
\end{document}

