\input{template.tex}

\begin{document}

    \begin{thm}{Exercise 1}{}
        Let $G = (V, c)$ be a flow network. Prove that flow is ``transitive'' in the following sense: if $r, s, t$ are vertices, and there is an $r$-$s$-flow of value $k$ and an $s$-$t$-flow of value $k$, then there is an $r$-$t$-flow of value $k$.
    \end{thm}

    \begin{proof}
        Note that there is an $r$-$s$-flow of value $k$ means that the value of the maximum $r$-$s$-flow is at least $k$, which also means that the value of the minimum $r$-$s$-cut is at least $k$. Similarly, the value of the minimum $s$-$t$-cut is also at least $k$.
        
        Now consider an $r$-$t$-cut. It is either an $r$-$s$-cut (if $s$ is not in the cut) or an $s$-$t$-cut (if $s$ is in the cut). So the capacity of the minimum $r$-$t$-cut is at least $k$. It follows that the value of the maximum $r$-$t$-flow is at least $k$, and thus there is an $r$-$t$-flow of value $k$.
    \end{proof}

    \begin{thm}{Exercise 3}{}
        Prove Menger’s Theorem. You have to prove two things: first, not both cases above can occur (this is rather easy); second, one of them must occur (this requires a tool from the lecture).
    \end{thm}
    \begin{proof}[Proof]
        Let $V(G) = \{v_1, \cdots \}$ and $s = v_p, t = v_q$. 
    
        We would like to construct a flow network $(V', s', t', c)$ where $V' = \{v_1, v_1', v_2, v_2', \cdots \}$ and
        $$c(u, v) = \begin{cases}
            1, \text{ if } \exists i, (u, v) = (v_i, v_i') \\
            \infty, \text{ if } \exists i, j, (u, v) = (v_i', v_j) \wedge (v_i, v_j) \in E \\
            0, \text{ otherwise }
        \end{cases}.$$
    
        And finally let $s' = v_p', t' = v_q$. Then:
    
        \begin{itemize}
            \item There are $k$ vertex disjoint paths $p_1, \cdots ,p_k$ in $G$ iff there is a flow $f$ in $(V', s', t', c)$ with $\text{val}(f) = k$, iff $\max \text{val}(f) \ge k$.
            \item There are $k-1$ vertices $v_{i_1}, \cdots ,v_{i{k-1}}$ in $V \setminus \{s, t\} $ such that $G - \{v_{i_1},\cdots , v_{i_{k-1}}\} $ contains no $s-t$ path iff there is a cut $S$ in $(V', s', t', c)$ with $\text{cap}(S) = k-1$ by making $v_{i_j} \in S$ and $v_{i_j}' \not\in S$ for all $j$, iff $\min \text{cap}(S) < k$.
        \end{itemize}
    
        By \textit{Max-Flow Min-Cut Theorem}, let $\max \text{val}(f) = \min \text{cap}(S) = l$. Then:
        \begin{itemize}
            \item Either $l \ge k$, resulting in $1$ holds while $2$ does not.
            \item Or $l < k$, resulting in $2$ holds while $1$ does not.
        \end{itemize}
    
        Therefore, \textit{exactly one} of the two statements is true.
    \end{proof}

    In the two exercises below, let $\Gamma(X)$ be the neighbors of $X$. 
    \begin{thm}{Exercise 4}{}
        Consider the induced bipartite subgraph $H_n[L_i\cup L_{i+1}]$, show that for $i<n/2$ the graph has a matching of size $|L_i|=\binom{n}{i}$
    \end{thm}
    \begin{proof}
        Use Hall's Theorem, the size of maximum matching equals $\min_{X\subseteq L_i}|L_i|-|X|+|\Gamma(X)|$. 

        Since in $H_n[L_i\cup L_{i+1}]$ the degree of each vertex in $L_i$ is $n-i$, 
        and that of each vertex in $L_{i+1}$ is $i+1$, there is $|X|(n-i)\leq|\Gamma(X)|(i+1)$. 
        As $i<n/2$, $|X|\leq|\Gamma(x)|\frac{i+1}{n-i}\leq|\Gamma(X)|$, and only if $|X|=0$ can the equality be achieved. 

        So there is $\min_{X\subseteq L_i}(|L_i|-|X|+|\Gamma(X)|)=|L_i|=\binom{n}{i}$. 
    \end{proof} 

    \begin{thm}{Exercise 5}{}
        Show that there are $\binom{n}{i}$ paths in $H_n$ starting at $L_i$ ending in $L_{n-i}$ and are disjoint. 
    \end{thm}
    \begin{proof}
        We first set a new point $s$ connected to all vertices in $L_i$ and a new point $t$ connected to all vertices in $L_{n-i}$. 
        
        Set the capacity of edges starting from $s$ or ending to $t$ be $1$, and the capacity of the rest be $\infty$. 
        Then there is a flow that, for edges whose capacity is $1$ the flow takes $1$; for the rest edges, 
        each in form of $(u,v), u\in L_k,v\in L_{k+1}$, the flow takes $\frac{\binom{n}{i}}{\binom{n}{k}(n-k)}$. 

        It is obvious that the flow is well-defined, that for each vertex (except for $s,t$) the flow in equals the flow out. 
        And the total flow is $\binom{n}{i}$. Besides, it is the maxflow since the flow out of $s$ is no more than $\binom{n}{i}$. 

        So there exists a min-cut of the graph that the size of the cut is $\binom{n}{i}$ as well. 
        The collection of the end point of each edge in the cut is a vertex cut, 
        so the size of the minimum vertex cut is $\binom{n}{i}$. 
        By Menger's Theorem, there are $\binom{n}{i}$ disjoint paths from $s$ to $t$, 
        by removing $s$ and $t$ of these paths, we get $\binom{n}{i}$ disjoint paths from $L_i$ to $L_{n-i}$ 
        
    \end{proof} 

    \begin{thm}{Exercise 6}{}
        Let $\nu(G)$ denote the size of a maximum matching of $G=(V,E)$.
        Show that a bipartite graph $G$ has at most $2^{\nu(G)}$ mimimum vertex covers.
    \end{thm}
    \begin{proof}
        From the Konig's Theorem, we know that the size of mimimum vertex cover is $\nu(G)$.
        Let $C$ be a minimum vertex cover.
        Then we can construct new minimum vertex cover by choosing vertices from $C$ and $V\setminus C$.
        In other words, all minimum vertex covers can be represented by $X\cup Y, X\subseteq C,Y\subseteq V\setminus C$.
        Denote $N(A)=\{b|\exists a\in A, \text{there is an edge between a and b}\}$.
        For all $X\subseteq C$, to construct a vertex cover, $Y$ must touch all edges touched by $C\setminus X$ but not by $X$.
        \begin{itemize}
            \item If $N(C\setminus X)\cap (C\setminus X)\ne \emptyset$, there does not exist such a $Y$.
            \item  If $N(C\setminus X)\cap (C\setminus X)= \emptyset$, then $Y$ must be at least $N(C\setminus X) \cap (V\setminus C)$ to be a vertex cover.
            To make $X\cap Y$ a minimum vertex cover, $Y$ has to be $N(C\setminus X) \cap (V\setminus C)$.
        \end{itemize}

        Since $X$ has $2^{\nu(G)}$ choices, $G$ has at most $2^{\nu(G)}$ mimimum vertex covers.
    \end{proof}

    Obviously, this is not true for general (non-bipartite) graphs: the triangle $K_3$ has $\nu(K_3) = 1$ but it has three minimum vertex covers. The five-cycle $C_5$ has $\nu(C_5) = 2$ but has five minimum vertex covers.

    \begin{thm}{Exercise 7}{}
        Is there a function $f \colon \mathbf{N_0} \rightarrow \mathbf{N_0}$ such that every graph with $\nu(G) = k$ has at most $f(k)$ minimum vertex covers? How small a function $f$ can you obtain?
    \end{thm}

    \begin{proof}[Solution]
        Suppose that we have a graph $G = (V, E)$ and one of its maximum matching $M \subseteq E$ with $|M| = \nu(G) = k$.
        
        We have the two following observations:
        
        \begin{itemize}
            \item For any vertex cover $C \subseteq V$ of $G$, for every edge in $M$ there must be at least one of its endpoint which is in $C$. Otherwise there exists an edge in $M$ such that neither of its endpoints is in $C$, which means that this edge is uncovered and therefore $C$ is not a vertex cover.
            \item For any vertex $v$ which is not matched, all of its neighbors must be matched, or the edge between $v$ and one of its unmatched neighbors can be added to the maximum matching and therefore $M$ is not maximum.
        \end{itemize}
        
        We now construct a vertex set $C_0 \subseteq V$ such that for every edge $(u, v)$ in $M$, either $u \in C_0$, or $v \in C_0$, or both $u, v \in C_0$. There are $3^k$ possible $C_0$ in total.
        
        For each possible $C_0$, note that it may not be a ``vertex cover'' by far. So we try to construct another vertex set $C_1$ from $C_0$. Let $C_1$ be an empty set at the beginning. From the second observation above, for every unmatched vertex $v$, there are two cases. If all of its neighbors are in $C_0$, then we do nothing, since every edge connected to $v$ is covered by vertices in $C_0$. Otherwise we add it into $C_1$ to cover the edges which $C_0$ didn't cover. Note that $C_1$ is {\it uniquely determined by $C_0$}.
        
        Let $\mathcal{C}$ be a family of vertex covers, which is initialized to empty. Now consider $C_0 \cup C_1$. We know that it is also uniquely determined by $C_0$. If it is a vertex cover, we add it to $\mathcal{C}$. There are at most $3^k$ vertex covers in $\mathcal{C}$, since there are $3^k$ possible $C_0$, and for some $C_0$ and its corresponding $C_1$, $C_0 \cup C_1$ may not be a vertex cover.
        
        Claim that any minimum vertex cover $C$ must belong to $\mathcal{C}$. Because from the first observation, we can let the unique $C_0$ be the matched vertices covered by $C$. And then unique $C_1$ can be constructed from $C_0$. $C_0 \cup C_1$ is the minimum vertex cover when $C_0$ is fixed. So $C = C_0 \cup C_1 \in \mathcal{C}$.
        
        So there are at most $3^k$ minimum vertex covers in total, and $f(k) = 3^k$. Also note that this upper bound is {\it tight}. Just consider the triangle $K_3$ --- it has $3 = 3^1 = 3^{\nu(K_3)}$ minimum vertex covers.
    \end{proof}

\end{document}