\input{template.tex}

\begin{document}
    
    Obviously, this is not true for general (non-bipartite) graphs: the triangle $K_3$ has $\nu(K_3) = 1$ but it has three minimum vertex covers. The five-cycle $C_5$ has $\nu(C_5) = 2$ but has five minimum vertex covers.

    \begin{thm}{}{}
        Is there a function $f \colon \mathbf{N_0} \rightarrow \mathbf{N_0}$ such that every graph with $\nu(G) = k$ has at most $f(k)$ minimum vertex covers? How small a function $f$ can you obtain?
    \end{thm}

    \begin{proof}[Solution]
        Suppose that we have a graph $G = (V, E)$ and one of its maximum matching $M \subseteq E$ with $|M| = \nu(G) = k$.
        
        We have the two following observations:
        
        \begin{itemize}
            \item For any vertex cover $C \subseteq V$ of $G$, for every edge in $M$ there must be at least one of its endpoint which is in $C$. Otherwise there exists an edge in $M$ such that neither of its endpoints is in $C$, which means that this edge is uncovered and therefore $C$ is not a vertex cover.
            \item For any vertex $v$ which is not matched, all of its neighbors must be matched, or the edge between $v$ and one of its unmatched neighbors can be added to the maximum matching and therefore $M$ is not maximum.
        \end{itemize}
        
        We now construct a vertex set $C_0 \subseteq V$ such that for every edge $(u, v)$ in $M$, either $u \in C_0$, or $v \in C_0$, or both $u, v \in C_0$. There are $3^k$ possible $C_0$ in total.
        
        For each possible $C_0$, note that it may not be a ``vertex cover'' by far. So we try to construct another vertex set $C_1$ from $C_0$. Let $C_1$ be an empty set at the beginning. From the second observation above, for every unmatched vertex $v$, there are two cases. If all of its neighbors are in $C_0$, then we do nothing, since every edge connected to $v$ is covered by vertices in $C_0$. Otherwise we add it into $C_1$ to cover the edges which $C_0$ didn't cover. Note that $C_1$ is {\it uniquely determined by $C_0$}.
        
        Let $\mathcal{C}$ be a family of vertex covers, which is initialized to empty. Now consider $C_0 \cup C_1$. We know that it is also uniquely determined by $C_0$. If it is a vertex cover, we add it to $\mathcal{C}$. There are at most $3^k$ vertex covers in $\mathcal{C}$, since there are $3^k$ possible $C_0$, and for some $C_0$ and its corresponding $C_1$, $C_0 \cup C_1$ may not be a vertex cover.
        
        Claim that any minimum vertex cover $C$ must belong to $\mathcal{C}$. Because from the first observation, we can let the unique $C_0$ be the matched vertices covered by $C$. And then unique $C_1$ can be constructed from $C_0$. $C_0 \cup C_1$ is the minimum vertex cover when $C_0$ is fixed. So $C = C_0 \cup C_1 \in \mathcal{C}$.
        
        So there are at most $3^k$ minimum vertex covers in total, and $f(k) = 3^k$. Also note that this upper bound is {\it tight}. Just consider the triangle $K_3$ --- it has $3 = 3^1 = 3^{\nu(K_3)}$ minimum vertex covers.
    \end{proof}


\end{document}

